---
title: ChamberFlux (working title)
subtitle: An adapted version of the R package "RespChamberFlux" to calculate gas fluxes measured with the PICARRO system (SUBTITLE TO BE ADAPTED)" 
author: "authors"
date: last-modified
format:
  html: 
    code-fold: true
  pdf:
    geometry: 
      - top=30mm
      - left=30mm
bibliography: 'bibliography.bib'
---

```{r}
#| label: load-pkgs
#| message: false

library("rlang")
library("changepoint")
library("nlme")
library("segmented")
library("tibble")
library("plyr")
library("dplyr")
library("purrr")
library("RespChamberProc")
library("devtools")
library("stringr")
library("ggplot2")
library("data.table")
library("lubridate") 
```

```{r}
#| label: project-setup
#| message: false
#| 

rel_pathname <- "Data_Jesus/" #"Data_Adrian/Agosto/19/"
fileName <- "JFAADS2174-20220531-080209-DataLog_User.dat" #set here file name

newpackagename <- "[NEWPACKAGENAME]" #enter here the name of the R package

#create folder with the name of the measurement archive to save results and plots therein
dir.create(paste0(rel_pathname,"results"))

results_dir <- paste0(rel_pathname,"results/",str_sub(fileName,end=-18))
dir.create(results_dir)
```

```{r}
#| label: read-and-prepare-data
#| message: false


ds0 <- fread(paste0(rel_pathname,fileName), sep ="auto")
## The logger is accumulating data from previous field campaigns. 
#  Here we subset data from a given field campaign. (Entrar hora del inicio de observationes y fin (convert to UTC))
ds <- subset(ds0, as.numeric(TIMESTAMP) >= as.numeric(as.POSIXctUTC("2022-05-01 00:00:00")) )
ds <- subset(ds, as.numeric(TIMESTAMP) <= as.numeric(as.POSIXctUTC("2025-04-15 23:00:00" )) )
```



# Introduction
## Background
- gas flux measurements
- Picarro

## Aims and structure of this article
In this article, we present *`r newpackagename`*, which is an adapted version of the R (@RSoftware) package *RespChamberFlux* (@RespChamberProc), suited for the use with the *Picarro* system (Reference) that measures the flux of various gases, including CO2, H2O, N2O, NH3, AND CH4.

We demonstrate the use of the package with data from a case study located in Córdoba, Spain (ADD STUDY SITE FIGURE).


# Methodology
All calculations were done using R Statistical Software version `r paste(version$major,version$minor,sep=".")` (@RSoftware).

# Results

## Case study: Data Jesus




```{r}
#| label: example-CO2-timeseries
#| fig-cap: An example time series of CO2
#| fig-width: 10
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false




```

# Discussion

# Conclusions



# References {.unnumbered}
